Model LF

### 2022-10-31 Final test.Rmd
Commit

@@

#### Shock variables 
shock_wage_ds_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_max_dp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_reg_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_part_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_kuld_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_prod_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_lf_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

@@

@@

COMMENT> 
BEHAVIORAL> prod_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock) = pr_0 + pr_1* TSDELTALOG(TSLAG(prod_shock,2)) + pr_2* TSDELTALOG(TSLAG(prod_shock,3))  + pr_8* LOG(TSLAG(dp_person,1)) + pr_9* TSLAG(s_h,1) + pr_10* LOG(TSLAG(prod_shock,1)) + pr_11 * d_2007q4 
COEFF> pr_0 pr_1 pr_2 pr_8 pr_9 pr_10 pr_11
STORE> coe(22)

COMMENT> 
BEHAVIORAL> prod_shock_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock_sens) = prs_0 + prs_1* TSDELTALOG(TSLAG(prod_shock,2)) + prs_2* TSDELTALOG(TSLAG(prod_shock,3))  + prs_8* LOG(TSLAG(dp_person,1)) + prs_9* TSLAG(s_h,1) + prs_10* LOG(TSLAG(prod_shock,1)) + prs_11 * d_2007q4
RESTRICT> prs_8 = 0.1
COEFF> prs_0 prs_1 prs_2 prs_8 prs_9 prs_10 prs_11
STORE> coe(24)

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod= prod_shock
if> shock_prod_model > 0
IDENTITY> prod
EQ> prod= prod_shock_sens
if> shock_prod_model > 0 & sens3_low > 0

@@

COMMENT> 
IDENTITY> prodk
EQ> prodk=prod * (yk/y)
IF> shock_prod_model > 0

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds = prodk_ds * (y_ds/yk_ds)
IF> shock_prod_model <= 0
IDENTITY> prod_ds
EQ> prod_ds =  prod - (alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3) + mean_prod
IF> shock_prod_model > 0

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_prod_model > 0

@@

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  lf_test1 = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$ur = ur

@@

lf_test_00 = S_model$simulation$lf_test
lf_test1_00 = S_model$simulation$lf_test1

wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds

@@

@@

@@

```{r}
plot(((unemp_07b - unemp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

**Macro effect without productivity**

>>>>

alpha_200 =reg_21$coefficients[1]
alpha_200=ts(alpha_120,start = c(2005,2), end = c(2020,1), frequency = 4 )

alpha_201=reg_21$coefficients[2]
alpha_201=ts(alpha_201,start = c(2005,2), end = c(2020,1), frequency = 4 )

alpha_202=reg_21$coefficients[3]
alpha_202=ts(alpha_202,start = c(2005,2), end = c(2020,1), frequency = 4 )

alpha_203=reg_21$coefficients[4]
alpha_203=ts(alpha_203,start = c(2005,2), end = c(2020,1), frequency = 4 )

mean_prodk= mean(prodk)
mean_prodk=ts(mean_prodk,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

#### Shock variables 
shock_wage_ds_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_max_dp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_reg_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_part_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_kuld_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_prod_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_lf_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_Verdonn_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

## Prod equations

```{r}
g_yk_ds= TSDELTALOG(yk_ds)
g_prodk_ds= TSDELTALOG(prodk_ds)

@@

COMMENT> 
IDENTITY> g_yk_ds
EQ> g_yk_ds = TSDELTALOG(yk_ds)

COMMENT> 
BEHAVIORAL> g_prodk_ds
TSRANGE 2005 4 2020 1
EQ> g_prodk_ds = phi_0 + phi_1* g_yk_ds + phi_2 * TSLAG(g_yk_ds,1) + phi_3* TSLAG(g_prodk_ds,1)
COEFF> phi_0 phi_1 phi_2 phi_3
STORE> coe(103)

@@

@@

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
IF> shock_Verdonn_model <= 0
IDENTITY> prod
EQ> prod= prod_ds + (alpha_150 + alpha_151*SD1 + alpha_152*SD2 + alpha_153*SD3) - mean_prod
IF> shock_Verdonn_model > 0

COMMENT> 
IDENTITY> prodk
EQ> prodk=prod * (yk_ds/y_ds)
IF> shock_Verdonn_model > 0

COMMENT> 
IDENTITY> prod_ds
EQ> prod_ds=prodk_ds * (y_ds/yk_ds)

IDENTITY> prodk_ds
EQ> prodk_ds= (1+g_prodk_ds)* TSLAG(prodk_ds)
IF> shock_Verdonn_model > 0

@@

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_Verdonn_model
EQ> shock_Verdonn_model = shock_Verdonn_model*1

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  lf_test1 = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  shock_Verdonn_model = TIMESERIES(c(shock_Verdonn_model),   
                        START=c(2005,2),FREQ=4),
  g_yk_ds = TIMESERIES(c(g_yk_ds),   
                        START=c(2005,3),FREQ=4),
  g_prodk_ds = TIMESERIES(c(g_prodk_ds),   
                        START=c(2005,3),FREQ=4)
)
```

@@

S_modelData$g_prodk_ds1 = g_prodk_ds

@@

lf_test_00 = S_model$simulation$lf_test
lf_test1_00 = S_model$simulation$lf_test1
g_prodk_ds_00 = S_model$simulation$g_prodk_ds
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds

g_prodk_ds_00 = S_model$simulation$g_prodk_ds

@@

plot(g_prodk_ds_00, col= "green"); lines(g_prodk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

## Baseline Vendonn

```{r}
shock_Verdonn_model_shock=shock_Verdonn_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_V <- list(

 shock_Verdonn_model = TIMESERIES(shock_Verdonn_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_V <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_V
                    )
```

```{r}
###Gengivelse af stød til model
part_V = Shock_V$simulation$part
unemp_V = Shock_V$simulation$unemp
komp_r_V = Shock_V$simulation$komp_r
part_V = Shock_V$simulation$part
yk_ds_V = Shock_V$simulation$yk_ds
pc_ds_V = Shock_V$simulation$pc_ds
wage_ds_t_V = Shock_V$simulation$wage_ds_t
ur_ds_V = Shock_V$simulation$ur_ds
emp_V = Shock_V$simulation$emp
yd_hk_ds_V = Shock_V$simulation$yd_hk_ds
pconk_ds_V= Shock_V$simulation$pconk_ds
tilpas_pr_V = Shock_V$simulation$tilpas_pr
u_ds_V = Shock_V$simulation$u_ds
part_V = Shock_V$simulation$part
nben_h_V = Shock_V$simulation$nben_h
wage_ds_V = Shock_V$simulation$wage_ds
dp_person_V = Shock_V$simulation$dp_person
kont_h_ratio_V = Shock_V$simulation$kont_h_ratio
unemp_V = Shock_V$simulation$unemp
nl_g_V = Shock_V$simulation$nl_g
inflation_V = Shock_V$simulation$inflation
lf_V = Shock_V$simulation$lf
yd_hk_ds_V = Shock_V$simulation$yd_hk_ds
wage_gap1_V = Shock_V$simulation$wage_gap1
wage_gap_V = Shock_V$simulation$wage_gap
prod_V = Shock_V$simulation$prod
prodk_ds_V = Shock_V$simulation$prodk_ds
```

```{r}
plot(prodk_ds_V, col= "green"); lines(prodk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ur_ds_V, col= "green"); lines(ur_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ur_ds_00, col= "green"); lines(ur_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
plot(((unemp_07b - unemp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Change in Unemployment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

**Macro effect without productivity and LF**
